Theories of deliberated choice

### 2023-06-18 simple.tex
Rm unuseful proof
A post fals, corrected

\subsection{An example and a discussion about observability}
The following toy example is inspired by an argument from \citet[p.~59]{railton_facts_2003}. Here is his argument.
\begin{quote}
An experiment in cognitive psychology reveals that when subjects observe two individuals taking a test, one of whom answers a high percentage of the early questions correctly but then falters, while the other does
poorly initially but then answers a high percentage of the later questions
correctly, the first is usually viewed as more able, even though in the end
each answers the same number of questions correctly in all. If the subjects had been asked which test-taker they would prefer as a math tutor,
they likely would have answered “The first,” and perhaps they would also
have been willing to pay a premium to secure his services. But if they
were to become convinced of the influence of sheer order on their evaluations of relative ability, they presumably would no longer want their
initial preference for the first test-taker to influence their choices – or
willingness to pay – in this way.
\end{quote}
\begin{example}[Math tutor]
	\label{ex:tutor}
	Let $I$ be a set of individuals desiring to evaluate two candidates $\set{m_1, m_2}$ for math tutoring.
	Consider one individual $i \in I$.
	Let ${\leadsto}(i, a_1)$ represent $i$ being shown a test of candidate $m_1$ wherein $m_1$ answers 70\% of the first half of questions correctly but then only 40\% of the other half correctly.
	Let ${\leadsto}(i, a_2)$ represent $i$ being shown a test of candidate $m_2$ wherein $m_2$ answers 45\% of the first half of questions correctly, then 75\% of the other half correctly.
%	Let ${\leadsto}(i, a_e)$ represent $i$ being given an explanation about the psychological phenomenon described in the quote above.
	Let ${\leadsto}(i, a_e)$ represent $i$ being given the following argument. “When tested, $m_1$ answers 70\% of the first half of questions correctly but then only 40\% of the other half correctly; whereas $m_2$ answers 45\% of the first half of questions correctly, then 75\% of the other half correctly. It follows than $m_1$ answers on average less well than $m_2$. Observing the candidates take the tests may yield a contrary impression; this is a well-known psychological phenomenon depending on the order of the questions that the candidates answer correctly.”
	Let $\prop_1$ represent the choice of $m_1$ and $\prop_2$ that of $m_2$.

	If the prediction described in the quote applies to $i$, the relation $\ileadsto$ is as follows, $\forall k \in \N^*$ (recall that for $\args \subseteq \allargs$, $\args^k$ represents the set of sequences of length $k$ using arguments from $\args$): $\forall \hist \in \set{a_e}^k, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_1, a_2}^k, \hist \ileadsto \prop_1$; $\forall \hist \in \set{a_1, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_2, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \allargs^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$. The values of ${\leadsto}(i, \hist)$ for $\hist = \emptyset$ and for $\hist \in \allargs^k \suchthat a_e \notin \histend$ are undetermined by the prediction, but whatever they are, $a_e$ is a decisive argument for $\prop_2$, hence, $i$’s deliberated choice is $\prop_2$.
\end{example}

@@

\section{Theories of deliberated choice}
This section assumes that an exposure protocol $(I, \allargs, {\leadsto})$ is defined, and defines theories of deliberated choice associated with that exposure protocol. We will start with very simple theories (\cref{sec:static}) in order to build an intuition about the conditions required on theories of deliberated choice, then justify the need for more complex theories (\cref{sec:lichtenstein}) and finally define more general theories of deliberated choice (\cref{sec:dynamic}).

@@

The following example illustrates this same point in a constrained setting which permits a complete definition of $\allargs$ and $\leadsto$.%, which permits defining the setting completely at the price of a reduced realism.
\begin{example}[A decision problem about two lotteries]
	\label{ex:lichtenstein}
	In a famous article about preference reversals, \citet{lichtenstein_reversals_2006} discuss an example involving two lotteries. The lottery $L_P$ lets the subject win four dollars with 99\% chance and lose ten cents with 1\% chance; in summary, $L_P = (.99, +\$4; .01, −\$0.1)$. The lottery $L_D$ is, using the same notations: $(.33, +\$16; .67, −\$2)$. The letter $P$ stands for probability: one salient aspect of $L_P$ is the very high chance of winning. The letter $D$ stands for dollar: one salient aspect of $L_D$ is the high gain it gives (compared to $P$) in dollar amount if the subject is lucky.

@@

\subsection{Form of theories (draft)}
Given an exposure protocol $(I, \allargs, {\leadsto})$, we want to phrase some claims under the form of a logical sentence $C$ such that:
if $C$ holds, then it implies something about the dj of some $i$;
if $C$ fails, it is possible to falsify it.

We can observe set $O$ that forms a function $f(i) = \set{\alpha \ileadsto \phi, \alpha' \ileadsto ¬\phi, …}$, with $\alpha \subset \alpha \subset …$ and with finite $O$.
Our second condition is that $¬C \implies \exists O \suchthat O \implies ¬C$.
For example, if $C$ is $\alpha \ileadsto \phi \lor \beta \leadsto[j] \phi$, $O$ is $\alpha \ileadsto ¬\phi \land \beta \leadsto ¬\phi$, then $O$ implies $¬C$.
As another example, $C$ being $\exists \alpha \suchthat \alpha \ileadsto \phi$ is unfalsifiable, as its negation is $\forall \alpha: \alpha \nileadsto \phi$, which requires infinite $O$.

Consider $\leadsto$ such that $\exists \ar, \phi \suchthat \forall i: \ar \ileadsto \phi$.
Then some suitable $C$ exists.
It is $\forall i: \ar \ileadstost \phi$.
If false, it is falsifiable.
Even though it is not provable by any $O$.

Now consider $\leadsto$ such that $\exists J, K \subset I \suchthat \ar \ileadstost[j] \phi, \ar' \ileadstost[k] \phi$.
Then no suitable $C$ exists?

@@

\subsection{Form of theories}
Given an exposure protocol $(I, \allargs, {\leadsto})$, recall that ${\leadsto} \in P^{I × \allhist}$.

Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\leadsto$, thus, $C \subseteq P^{I × \allhist}$.
The claim holds iff ${\leadsto} \in C$.
When writing $C$ as a formula, it is intended to mean the set $\set{{\leadsto} \in P^{I × \allhist} \suchthat C({\leadsto})}$.

Given a pair $(I, \allargs)$, a general observation $O$ is a finite subset of $I × \allhist × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in O: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
General observations are the a priori possible observations, that is, those that can be considered possible when nothing is known about $\leadsto$.
Let $S_O = \set{f \in P^{I × \allhist} \suchthat O \subseteq f}$ denote the possibilities for $\leadsto$ compatible with the observations.

A claim $C$ is falsifiable iff $\exists O \suchthat O \implies ¬C$, by which I mean $S_O \cap C = \emptyset$.
\begin{example}
	$(\ar) \ileadsto \phi \lor (\ar, \ar) \ileadsto \phi \lor …$ is not falsifiable.
%	Its negation is $\forall k: (\ar^k) \nileadsto \phi$.
%	The claim represents the set $\set{{\leadsto} \in P^{I × \allhist} \suchthat (\ar) \ileadsto \phi \lor  (\ar, \ar) \ileadsto \phi \lor …}$.
	Given any $O$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in O} \card{\hist} + 1$. Pick any $\leadsto$ such that $O \subset {\leadsto} \land (\ar)^l \ileadsto \phi$. We have ${\leadsto} \in S_O \cap C ≠ \emptyset$.
\end{example}
\begin{example}
	$(\ar) \ileadsto \phi \lor (\ar') \ileadsto \phi$ is not falsifiable.
	Given any $O$, it may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any $\leadsto$ such that $O \subset {\leadsto} \land t \in {\leadsto}$. We have ${\leadsto} \in S_O \cap C ≠ \emptyset$.
\end{example}
\begin{example}[Fals. but shouldn’t]
	$\hist \ileadsto[j] \phi \land [(\ar) \ileadsto \phi \lor (\ar, \ar) \ileadsto \phi \lor …]$ is falsifiable.
	Consider $O = \set{(j, \hist, ¬\phi)}$.
\end{example}
\begin{example}[Fals. but shouldn’t, better]
	\label{ex:fbs}
	$\hist \ileadsto[j] \phi \land [(\ar) \ileadsto \phi \lor (\ar') \ileadsto \phi]$ is falsifiable.
	Consider $O = \set{(j, \hist, ¬\phi)}$.
\end{example}
\begin{example}
	$\forall i: \ar \ileadstost \phi$ is falsifiable.
	Consider any $i \in I$ and $O = \set{(i, (\ar), ¬\phi)}$.
\end{example}

\Cref{ex:fbs} shows that this definition of falsifiability is wrong.
We now say that $C$ is falsifiable iff $\forall {\leadsto} \in P^{I × \allhist}: ¬C({\leadsto}) \implies \exists O \subseteq {\leadsto} \suchthat O \implies ¬C$, meaning that
$\forall {\leadsto} \notin C: \exists O \subseteq {\leadsto} \suchthat S_O \cap C = \emptyset$.
\begin{example}
	$(\ar) \ileadsto \phi \lor  (\ar, \ar) \ileadsto \phi \lor …$ is falsifiable.
	Consider any ${\leadsto} \notin C$, thus satisfying $\exists k \suchthat (\ar)^k \nileadsto \phi$. Consider $O = \set{(i, (\ar)^k, {\leadsto}(i, (\ar)^k) ≠ \phi)}$, thus with $O \subset {\leadsto}$. We have $S_O \cap C = \emptyset$: consider any $O \subset f$, it is not in $C$.
\end{example}
\begin{example}
	$(\ar) \ileadsto \phi \lor (\ar') \ileadsto \phi$ is not falsifiable.
	Consider any ${\leadsto} \notin C$, thus satisfying $(\ar) \nileadsto \phi \land (\ar') \nileadsto \phi$.
	Consider any $O \subseteq {\leadsto}$ and let us prove that $S_O \cap C ≠ \emptyset$.
	By definition of a general observation, $O$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any $f$ such that $O \subset {f} \land t \in {f}$. We have ${f} \in S_O \cap C ≠ \emptyset$.
\end{example}
\begin{example}[TODO]
	$\hist \ileadsto[j] \phi \land [(\ar) \ileadsto \phi \lor (\ar, \ar) \ileadsto \phi \lor …]$ is not falsifiable?
	Consider any ${\leadsto} \notin C$, thus satisfying $\hist \nileadsto[j] \phi \lor [(\ar) \nileadsto \phi \land (\ar, \ar) \nileadsto \phi \land …]$.
	Consider $O = \set{(j, \hist, ¬\phi)}$.
\end{example}

@@

An argumentative theory claims that whenever some of its arguments fail to convince $i$ of choosing $\pga$, it can argue something else.
It is said to be truthful iff this claim is correct.
More precisely, its claims are about paths of the sort $\hist = (\arga, …, \ar_2, …, \ar_3, …)$ where $\ar_2 \in \dgi(\arga)$, $\ar_3 \in \dgi(\ar_2)$, …
The following definition makes this precise by mandating that whenever increasing subsequences of $\hist$, involving arguments $\ar_j$ proposed by the theory, are not convincing, then the theory is able to produce yet another argument in defense of its claim.%
\footnote{Intuition.
If $a_1$, used by the theory, is not decisive, then the theory has an answer, namely, $a_2$, which works at least temporarily.
If $a_1$ used by th is not dec, and $a_2$ used by th is not dec *in the same sequence*, then $a_3$ needs to defend *in the same sequence*.
$(…, a_1)$ NO and $(…, a_1, …, a_2)$ NO then $a_3$ defends it.
$\alpha$ of the form $(\alpha^1, \alpha^2)$ where $a_1$ in end of $α^1$ NO and $a_2$ in end of $α^2$ NO.}
\begin{definition}[Truthfulness]
	\label{def:truth}
	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\leadsto})$ is \emph{truthful} iff 
	$\forall i \in I, \hist \in \allhist, n \in \N, k \in \intvl{1, \card \hist}^n, \ar \in \allargs^n$:
	\begin{equation}
		\left.\begin{aligned}
			&\ar_1 = \arga \\
			&\forall 1 ≤ j < n: \ar_{j + 1} = \dg(\ar_j, α_{\intvl{1, k_j}}) \in \histbend{k_{j + 1}} \\
			&\forall 1 ≤ j ≤ n: \restr{\hist}{\intvl{1, k_j}} \nileadsto \pga
		\end{aligned}\right\}
		⇒ \dg(\ar_n, \hist) ≠ \emptyset.
	\end{equation}
\end{definition}
Given the paths $\alpha, \alpha'$, the sequence $(\alpha, \alpha')$ denotes a path constituted of the arguments in $\alpha$ followed by the arguments of $\alpha'$.
\begin{axiom}[Answerability-1]
	$\forall …$:
	\begin{equation}
		\left.\begin{aligned}
			&(\ar_4, \ar_2, \ar) \nileadsto \pga \\
			&(\ar_4, \ar_2, \ar, \ar_3) \ileadstost \pga \\
			&(\ar_5, \ar_2, \ar) \nileadsto \pga
		\end{aligned}\right\}
		⇒ (\ar_5, \ar_2, \ar, \ar_3) \ileadstost \pga.
	\end{equation}
\end{axiom}
Requires excluding:
	\begin{equation}
		\left.\begin{aligned}
			&(\ar_4, \ar_2, \ar) \nileadsto \pga \\
			&(\ar_4, \ar_2, \ar, \ar_3, \ar') \ileadsto \pga \\
			&(\ar_5, \ar_2, \ar) \nileadsto \pga\\
			&(\ar_5, \ar_2, \ar, \ar_3, \ar') \nileadsto \pga.
		\end{aligned}\right\}
	\end{equation}

>>>>

\subsection{An example and a discussion about observability}
The following toy example is inspired by an argument from \citet[p.~59]{railton_facts_2003}. Here is his argument.
\begin{quote}
An experiment in cognitive psychology reveals that when subjects observe two individuals taking a test, one of whom answers a high percentage of the early questions correctly but then falters, while the other does
poorly initially but then answers a high percentage of the later questions
correctly, the first is usually viewed as more able, even though in the end
each answers the same number of questions correctly in all. If the subjects had been asked which test-taker they would prefer as a math tutor,
they likely would have answered “The first,” and perhaps they would also
have been willing to pay a premium to secure his services. But if they
were to become convinced of the influence of sheer order on their evaluations of relative ability, they presumably would no longer want their
initial preference for the first test-taker to influence their choices – or
willingness to pay – in this way.
\end{quote}
\begin{example}[Math tutor]
	\label{ex:tutor}
	Let $I$ be a set of individuals desiring to evaluate two candidates $\set{m_1, m_2}$ for math tutoring.
	Consider one individual $i \in I$.
	Let ${\allleadsto}(i, a_1)$ represent $i$ being shown a test of candidate $m_1$ wherein $m_1$ answers 70\% of the first half of questions correctly but then only 40\% of the other half correctly.
	Let ${\allleadsto}(i, a_2)$ represent $i$ being shown a test of candidate $m_2$ wherein $m_2$ answers 45\% of the first half of questions correctly, then 75\% of the other half correctly.
%	Let ${\allleadsto}(i, a_e)$ represent $i$ being given an explanation about the psychological phenomenon described in the quote above.
	Let ${\allleadsto}(i, a_e)$ represent $i$ being given the following argument. “When tested, $m_1$ answers 70\% of the first half of questions correctly but then only 40\% of the other half correctly; whereas $m_2$ answers 45\% of the first half of questions correctly, then 75\% of the other half correctly. It follows than $m_1$ answers on average less well than $m_2$. Observing the candidates take the tests may yield a contrary impression; this is a well-known psychological phenomenon depending on the order of the questions that the candidates answer correctly.”
	Let $\prop_1$ represent the choice of $m_1$ and $\prop_2$ that of $m_2$.

	If the prediction described in the quote applies to $i$, the relation $\ileadsto$ is as follows, $\forall k \in \N^*$ (recall that for $\args \subseteq \allargs$, $\args^k$ represents the set of sequences of length $k$ using arguments from $\args$): $\forall \hist \in \set{a_e}^k, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_1, a_2}^k, \hist \ileadsto \prop_1$; $\forall \hist \in \set{a_1, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_2, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \allargs^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$. The values of ${\allleadsto}(i, \hist)$ for $\hist = \emptyset$ and for $\hist \in \allargs^k \suchthat a_e \notin \histend$ are undetermined by the prediction, but whatever they are, $a_e$ is a decisive argument for $\prop_2$, hence, $i$’s deliberated choice is $\prop_2$.
\end{example}

@@

\section{Theories of deliberated choice}
This section assumes that an exposure protocol $(I, \allargs, {\allleadsto})$ is defined, and defines theories of deliberated choice associated with that exposure protocol. We will start with very simple theories (\cref{sec:static}) in order to build an intuition about the conditions required on theories of deliberated choice, then justify the need for more complex theories (\cref{sec:lichtenstein}) and finally define more general theories of deliberated choice (\cref{sec:dynamic}).

@@

The following example illustrates this same point in a constrained setting which permits a complete definition of $\allargs$ and $\allleadsto$.%, which permits defining the setting completely at the price of a reduced realism.
\begin{example}[A decision problem about two lotteries]
	\label{ex:lichtenstein}
	In a famous article about preference reversals, \citet{lichtenstein_reversals_2006} discuss an example involving two lotteries. The lottery $L_P$ lets the subject win four dollars with 99\% chance and lose ten cents with 1\% chance; in summary, $L_P = (.99, +\$4; .01, −\$0.1)$. The lottery $L_D$ is, using the same notations: $(.33, +\$16; .67, −\$2)$. The letter $P$ stands for probability: one salient aspect of $L_P$ is the very high chance of winning. The letter $D$ stands for dollar: one salient aspect of $L_D$ is the high gain it gives (compared to $P$) in dollar amount if the subject is lucky.

@@

\subsection{Form of theories (draft)}
Given an exposure protocol $(I, \allargs, {\allleadsto})$, we want to phrase some claims under the form of a logical sentence $C$ such that:
if $C$ holds, then it implies something about the dj of some $i$;
if $C$ fails, it is possible to falsify it.

We can observe set $O$ that forms a function $f(i) = \set{\alpha \ileadsto \phi, \alpha' \ileadsto ¬\phi, …}$, with $\alpha \subset \alpha \subset …$ and with finite $O$.
Our second condition is that $¬C \implies \exists O \suchthat O \implies ¬C$.
For example, if $C$ is $\alpha \ileadsto \phi \lor \beta \allleadsto[j] \phi$, $O$ is $\alpha \ileadsto ¬\phi \land \beta \allleadsto ¬\phi$, then $O$ implies $¬C$.
As another example, $C$ being $\exists \alpha \suchthat \alpha \ileadsto \phi$ is unfalsifiable, as its negation is $\forall \alpha: \alpha \nileadsto \phi$, which requires infinite $O$.

Consider $\allleadsto$ such that $\exists \ar, \phi \suchthat \forall i: \ar \ileadsto \phi$.
Then some suitable $C$ exists.
It is $\forall i: \ar \ileadstost \phi$.
If false, it is falsifiable.
Even though it is not provable by any $O$.

Now consider $\allleadsto$ such that $\exists J, K \subset I \suchthat \ar \ileadstost[j] \phi, \ar' \ileadstost[k] \phi$.
Then no suitable $C$ exists?

@@

\subsection{Form of theories}
Given an exposure protocol $(I, \allargs, {\allleadsto})$, recall that ${\allleadsto} \in P^{I × \allhist}$.

Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\allleadsto$, thus, $C \subseteq P^{I × \allhist}$.
When writing $C$ as a formula, it is intended to mean the set $\set{{\allleadstog} \in P^{I × \allhist} \suchthat C({\allleadstog})}$.

Given a pair $(I, \allargs)$, a general observation $O$ is a right unique finite subset of $(I × \allhist) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in O: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
General observations are the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
Let $S_O = \set{{\allleadstog} \in P^{I × \allhist} \suchthat O \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.

A claim $C$ is falsifiable iff $\exists O \suchthat O \implies ¬C$, by which I mean $S_O \cap C = \emptyset$.
\begin{example}
	$(\ar) \ileadstog \phi \lor (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
%	Its negation is $\forall k: (\ar^k) \nileadsto \phi$.
%	The claim represents the set $\set{{\allleadsto} \in P^{I × \allhist} \suchthat (\ar) \ileadsto \phi \lor  (\ar, \ar) \ileadsto \phi \lor …}$.
	Given any $O$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in O} \card{\hist} + 1$. Pick any $\allleadstog$ such that $O \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$. We have ${\allleadstog} \in S_O \cap C ≠ \emptyset$.
\end{example}
\begin{example}
	$(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
	Given any $O$, it may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any $\allleadstog$ such that $O \subset {\allleadstog} \land t \in {\allleadstog}$. We have ${\allleadstog} \in S_O \cap C ≠ \emptyset$.
\end{example}
\begin{example}[Fals. but shouldn’t]
	\label{ex:fbs}
	$\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is falsifiable.
	Consider $O = \set{(j, \hist, ¬\phi)}$.
\end{example}
\begin{example}
	$\forall i: \ar \ileadstostg \phi$ is falsifiable.
	Consider any $i \in I$ and $O = \set{(i, (\ar), ¬\phi)}$.
\end{example}
\Cref{ex:fbs} shows that this definition of falsifiability is wrong.

We now say that $C$ is falsifiable iff $\forall {\allleadstog} \in P^{I × \allhist}: ¬C({\allleadstog}) \implies \exists O \subseteq {\allleadstog} \suchthat O \implies ¬C$, meaning that
$\forall {\allleadstog} \notin C: \exists O \subseteq {\allleadstog} \suchthat S_O \cap C = \emptyset$.
\begin{example}
	$(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is falsifiable.
	Consider any ${\allleadstog} \notin C$, thus satisfying $\exists k \suchthat (\ar)^k \nileadstog \phi$. Consider $O = \set{(i, (\ar)^k, {\allleadstog}(i, (\ar)^k) ≠ \phi)}$, thus with $O \subset {\allleadstog}$. We have $S_O \cap C = \emptyset$: consider any $O \subset f$, it is not in $C$.
\end{example}
\begin{example}
	\label{ex:unfals}
	$(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
	Consider any ${\allleadstog} \notin C$, thus satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
	Consider any $O \subseteq {\allleadstog}$ and let us prove that $S_O \cap C ≠ \emptyset$.
	By definition of a general observation, $O$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any $f$ such that $O \subset {f} \land t \in {f}$. We have ${f} \in S_O \cap C ≠ \emptyset$.
\end{example}
\begin{example}
	$\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
	Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
	\Cref{ex:unfals} concludes.
\end{example}

Given an exposure protocol $\allleadsto$, deliberated choices are represented by an element $\pi({\allleadsto}) \subseteq I × P$ which is right unique (meaning that $\forall i \in I: \card{\pi({\allleadsto})(i)} ≤ 1$).
Equivalently, let $(P \cup \set{\emptyset})^I$ denote the right unique relations over $I × P$; and then the deliberated choices are an element $\pi({\allleadsto}) \in (P \cup \set{\emptyset})^I$.
We say that $C$ is informative iff $\exists {\allleadstog} \in (P \cup \set{\emptyset})^I \suchthat C \implies ¬{\allleadstog}$, meaning that $\pi(C) = \set{\pi(\allleadstog) \suchthat {\allleadstog} \in C} ≠ (P \cup \set{\emptyset})^I$.

Given an exposure protocol $\allleadsto$, we say that a claim $C$ holds iff $C \ni {\allleadsto}$.
$C$ is $\allleadsto$-suitable iff it is informative and falsifiable and ${\allleadsto} \in C$.

The following theorem verifies that when $C$ holds, it will not be falsified ex post (though it may be (a priori) falsifiable).
\begin{theorem}
	\label{th:ex-post}
	$\forall C \ni {\allleadsto}: \nexists O \subseteq {\allleadsto} \suchthat S_O \cap C = \emptyset$.
\end{theorem}
\begin{proof}
	We have, $\forall C \suchthat C \ni {\allleadsto}, \forall O \subseteq {\allleadsto}$: $O \subseteq {\allleadsto} \in C$, equivalently, ${\allleadsto} \in S_O \cap C$, thus $S_O \cap C ≠ \emptyset$.
\end{proof}
Therefore, falsifiability guarantees that a claim holds if, and only if, it is not a posteriori falsifiable.
\begin{theorem}
	\label{th:holdsiff}
	For all falsifiable $C$: ${\allleadsto} \in C$ iff $\nexists O \subseteq {\allleadsto} \suchthat S_O \cap C = \emptyset$.
\end{theorem}
\begin{proof}
	Consider any falsifiable $C$.
	By definition of falsifiability, $\forall {\allleadstog}: \nexists O \subseteq {\allleadstog} \suchthat S_O \cap C = \emptyset \implies {\allleadstog} \in C$.
	In particular,
	$\nexists O \subseteq {\allleadsto} \suchthat S_O \cap C = \emptyset \implies {\allleadsto} \in C$.
	The reverse implication is proven by \cref{th:ex-post}.
\end{proof}
Note that the reverse implication of $\cref{th:holdsiff} does not hold: a claim may hold and be not a posteriori falsifiable but be not a priori falsifiable.

\begin{example}[To be corrected]
Consider any $\allleadsto$ such that $\exists \ar, \phi \suchthat \forall i: \ar \ileadstost \phi$.
Then some suitable $C$ exists, for example, $\forall i: \ar \ileadstost \phi$.
Note that it is falsifiable but not verifiable (that is, no $O$ implies $C$).
\end{example}

\begin{example}[To be corrected]
Now consider $\allleadsto$ such that $\exists J, K \subset I \suchthat \forall j \in J: \ar \ileadstost[j] \phi \land \forall k \in K: \ar' \ileadstost[k] \phi$.
Then some suitable $C$ exists, for example, $\ar \ileadstost[j] \phi$.
\end{example}

@@

An argumentative theory claims that whenever some of its arguments fail to convince $i$ of choosing $\pga$, it can argue something else.
It is said to be truthful iff this claim is correct.
More precisely, its claims are about paths of the sort $\hist = (\arga, …, \ar_2, …, \ar_3, …)$ where $\ar_2 \in \dgi(\arga)$, $\ar_3 \in \dgi(\ar_2)$, …
The following definition makes this precise by mandating that whenever increasing subsequences of $\hist$, involving arguments $\ar_j$ proposed by the theory, are not convincing, then the theory is able to produce yet another argument in defense of its claim.%
\footnote{Intuition.
If $a_1$, used by the theory, is not decisive, then the theory has an answer, namely, $a_2$, which works at least temporarily.
If $a_1$ used by th is not dec, and $a_2$ used by th is not dec *in the same sequence*, then $a_3$ needs to defend *in the same sequence*.
$(…, a_1)$ NO and $(…, a_1, …, a_2)$ NO then $a_3$ defends it.
$\alpha$ of the form $(\alpha^1, \alpha^2)$ where $a_1$ in end of $α^1$ NO and $a_2$ in end of $α^2$ NO.}
\begin{definition}[Truthfulness]
	\label{def:truth}
	An argumentative theory $(\pga, \arga, \dg)$ for the exposure protocol $(I, \allargs, {\allleadsto})$ is \emph{truthful} iff 
	$\forall i \in I, \hist \in \allhist, n \in \N, k \in \intvl{1, \card \hist}^n, \ar \in \allargs^n$:
	\begin{equation}
		\left.\begin{aligned}
			&\ar_1 = \arga \\
			&\forall 1 ≤ j < n: \ar_{j + 1} = \dg(\ar_j, α_{\intvl{1, k_j}}) \in \histbend{k_{j + 1}} \\
			&\forall 1 ≤ j ≤ n: \restr{\hist}{\intvl{1, k_j}} \nileadsto \pga
		\end{aligned}\right\}
		⇒ \dg(\ar_n, \hist) ≠ \emptyset.
	\end{equation}
\end{definition}
Given the paths $\alpha, \alpha'$, the sequence $(\alpha, \alpha')$ denotes a path constituted of the arguments in $\alpha$ followed by the arguments of $\alpha'$.
\begin{axiom}[Answerability-1]
	$\forall …$:
	\begin{equation}
		\left.\begin{aligned}
			&(\ar_4, \ar_2, \ar) \nileadsto \pga \\
			&(\ar_4, \ar_2, \ar, \ar_3) \ileadstost \pga \\
			&(\ar_5, \ar_2, \ar) \nileadsto \pga
		\end{aligned}\right\}
		⇒ (\ar_5, \ar_2, \ar, \ar_3) \ileadstost \pga.
	\end{equation}
\end{axiom}
Requires excluding:
	\begin{equation}
		\left.\begin{aligned}
			&(\ar_4, \ar_2, \ar) \nileadsto \pga \\
			&(\ar_4, \ar_2, \ar, \ar_3, \ar') \ileadsto \pga \\
			&(\ar_5, \ar_2, \ar) \nileadsto \pga\\
			&(\ar_5, \ar_2, \ar, \ar_3, \ar') \nileadsto \pga.
		\end{aligned}\right\}
	\end{equation}
